---
title: "MarineGEO Data Submission Report"
output: html_document
---

**Report date:**

**Project affiliation:**

**Data provider:**

This report documents whether the data submission passes MarineGEO's quality assurance/quality control tests. If your submission failed one of the tests, you can view which protocol and sheet failed the test. Please update your data to fix any issues based on this information. If you cannot determine how to interpret a result, modify your data, or believe your data should be able to pass the tests, email MarineGEO (marinegeo@si.edu). 

Once you've addressed any issues(s), resubmit ONLY the data associated with the failed submission. 

## Summary

The table below summarizes our QA/QC tests for each file uploaded. If any file did not pass a test, additional information will be provided below detailing the nature of the failed test, and if it is necessary for the data to be updated, which excel sheet, column, and row should be modified. 

```{r echo=FALSE}

colnames(QA_summary) <- gsub("_", " ", colnames(QA_summary))

kable(
  QA_summary
)

```

## QA Test Details

If any files failed a QA test, a description of the test and the next steps to take are located below. 

```{r echo=FALSE, results='asis'}
 
if(nrow(QA_results$id_relationships)>0){
  id_warnings <- filter(warnings, title %in% QA_results$id_relationships$test)
  
  for(i in 1:nrow(id_warnings)){
    warning <- id_warnings[i,]
    result <- filter(QA_results$id_relationships, test == warning$title)
    
    cat("###", warning$title, 
        "\n",
        warning$message, "\n", "\n")
    
    # cat("**", paste(result$filename, collapse=", "), "**", sep="")
    
    print(   
      kable(
        result %>%
          select(filename, sheet_name, column_name, row_numbers, value)
      )
    )
    
    cat("\n", "\n")
    
  }
  
}
 
if(nrow(QA_results$numeric)>0){
  id_warnings <- filter(warnings, title %in% QA_results$numeric$test)
  
  for(i in 1:nrow(id_warnings)){
    warning <- id_warnings[i,]
    result <- filter(QA_results$numeric, test == warning$title)
    
    cat("###", warning$title, 
        "\n",
        warning$message, "\n", "\n")
    
    print(   
      kable(
        result %>%
          select(filename, sheet_name, column_name, row_numbers)
      )
    )
    
    cat("\n", "\n")
    
  }
  
}


```

## Visualizations

```{r echo=FALSE}

for(protocol in numeric_plots){
  print(protocol)
}

```